---
title: "R Notebook"
output: html_notebook
---
Notes: when doing a=0.9995 with around steps = 40,000 we get M = 5000 and expected was 4000. 
as a -> 1, with fixed steps = 40,000 we end up with worse and worse M's sorta proportional to the expected. 
  a= 0.9995: "Suggested M: 5701.000000, expected 3999.000000"
  a= 0.995:  "Suggested M: 532.000000, expected 399.000000"
  a=0.95: "Suggested M: 51.000000, expected 39.000000"
with steps = 40 * t_exp:
  a=0.25: "Suggested M: 5.000000, expected 1.666667"
  a=0.5: "Suggested M: 4.000000, expected 3.000000"
  a=0.75: 
  a=0.9: "Suggested M: 21.000000, expected 19.000000"
-> steps = 40 * t_exp actually better than a ton of steps in some cases, due to selection of C?
  
  
```{r}
# Dependencies
library(ggplot2)
library(LaplacesDemon)
source("./generic.R")
source("./deshMethod.R")
```

```{r}
states_visited <- c()
acfs <- c()
```
```{r}
# Specific to autoregression 
a = 0.95
b = 2
exp_m <- 1 + 2*(a/(1-a))
#steps = 40*exp_m
steps = 10000

get_next_step <- function(prev) {
  w <- rnorm(n=1, mean=0, sd=1)
  next_val <- a * prev + b * w
  return(next_val)
}

get_init_state <- function() {
  init_sd <- b^2 / (1-a^2)
  init_state <- rnorm(n=1, mean=0, sd=init_sd)
  return(init_state)
}

states_visited <- asim(get_init_state(), get_next_step, steps)
```
```{r}
exp_sd <- b^2 / (1-a^2)
sprintf("Mean: %f, Variance: %f, expected variance: %f", mean(states_visited), sd(states_visited)^2, exp_sd)
state_df <- data.frame(states_visited)
ggplot(state_df, aes(x=states_visited)) + geom_histogram() + stat_function(fun = dnorm,args = with(state_df, c(mean = 0, sd=exp_sd)))
```

```{r}
c <- 4 # since we expect an exponential here?
my_acfs <- c_est_series(states_visited)
```

```{r}
M_upper_bound <- 6000
triangle_df <- find_m(my_acfs, c, M_upper_bound)
length(triangle_df)
ggplot(triangle_df, aes(x=poss_Ms)) + geom_point(aes(y=ct_ints, color="forestgreen"), size=0.75) + geom_line(aes(y=ct_ints,color="forestgreen")) + geom_line(aes(y=poss_Ms, color="blue")) + ggtitle("Comparing M to c*Tau_int with c=6") + scale_color_manual(name = "", labels = c("M", "c*tau_int(M)"),values = c("forestgreen", "blue"))
m_suggest <- triangle_df[triangle_df$poss_Ms >= triangle_df$ct_ints,]
m_suggest <- m_suggest$poss_Ms[1]
sprintf("Suggested M: %f, expected %f", m_suggest, exp_m)
```
```{r}
M <- m_suggest
wind_df <- apply_window(lambda, my_acfs, M)
```
```{r}
max_x <- 300


plot_df <- wind_df[1:max_x,]
exp_ac <- a ^ plot_df$Lag
plot_df$exp_ac <- exp_ac
```
```{r}
ggplot(plot_df, aes(x=Lag)) + geom_point(aes(y=C_orig, color="black"), size=0.25) + geom_line(aes(y=C_orig, color="black")) + geom_point(aes(y=exp_ac, color="deeppink"), size=0.25) + geom_line(aes(y=exp_ac, color="deeppink")) +ggtitle("Expected Autocorrelation vs. Heuristic") + scale_color_manual(name = "", labels = c("Heuristic", "Expected"),values = c("black", "deeppink")) + xlab("Lag") + ylab("C")
```
```{r}
IAT(states_visited)
```


```{r}

```


NEW METHOD TEST 1: PIECEWISE       -----------------------
```{r}
x_test <- seq(0,10, by= 0.1)
y_test <- generate_piecewise(x_test)
plot(x_test, y_test, pch = 19)
mod_test <- lm(y_test ~ x_test)
#x[1:100]
```
```{r}
library(gsignal)
# new scaling region algorithm
n <- 10 # chosen
p <- 1 # chosen
q <- 2 # chosen
lim1 <- 9
results <- desh_method(x_test, y_test, lim1, n, p, q)
```

```{r}
results
vals <- get_slopes_sides(results)
vals
```
NEW METHOD TEST 2       -----------------------
```{r}
x_quad <- seq(0,2, by= 0.05)
y_quad <- x_quad ^ 2
n <- 10 # chosen
p <- 1 # chosen
q <- 2 # chosen
results_quad <- desh_method(x_quad, y_quad, length(x_quad)-1, n, p, q)
vals <- get_slopes_sides(results_quad)
vals
```
```{r}
acf_df <- c_est_series(states_visited)
acf_df
```
```{r}
lim <- x[which(acf_df$acf <= 0)][1]
y <- get_log(acf_df$acf)
x <- c(0:length(y))
```
```{r}
exp_m <- 1 + 2*(a/(1-a))
to_plot <- data.frame(x[1:70], y[1:70], acf_df$acf[1:70])
colnames(to_plot) <- c("x", "y", "acf")
to_plot
ggplot(to_plot, aes(x=x, y=y)) + geom_point()
ggplot(to_plot, aes(x=x, y=acf)) + geom_point() + geom_line()
```
```{r}
n <- 10 # chosen
p <- 1 # chosen
q <- 1 # chosen
#lims <- length(x) / 50
lim <- 2 * lim
results_ar1 <- desh_method(x,y, lim, n, p, q)

```
```{r}
results_ar1$xR[which.max(results_ar1$new_weights)]
results_ar1
vars_ar1 <- get_slopes_sides(results_ar1)
vars_ar1
```
```{r}
Ωzzzzzz
mine <- vars_ar1$best_rhs
```
```{r}
iat <- IAT(states_visited)
sprintf("a= %f: Expected= %f, Mine= %f, IAT function= %f", a, exp_m, mine, iat)
```

